Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-03 lids/twittersearchwrap/paper/paper.tex

Topics trending worldwide and in Germany at Twitter retrieved at February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

@@

The goal of our evaluation was to examine the stability of the entity
annotations over time. To achieve this, we have repeatedly executed the same set
of queries using the retrieved trending topics given in Table \ref{tbl:terms}
as input queries for the evaluation. The set of queries was executed twice per
hour in a 24 hour time frame starting from the moment the topics were identified
and retrieved as trending topics. In a first step we have filtered the result
sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains. We have then evaluated the results with respect to several measures:

>>>>

Topics trending worldwide and in Germany at Twitter retrieved on February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

@@

The goal of our evaluation was to examine the stability of the entity
annotations over time. To achieve this, we have repeatedly executed the same set
of queries and saved the returned data. Two methods for this data acquisition
were identified: \begin{definition}[Data Acquisition Methods]
\begin{itemize}
\item {\bf Temporal Sliding Window}\newline The query is executed and the n
most recent results are retrieved every t minutes. The Temporal Sliding Window
method may lead to duplicate messages in the retrieved documents, but needs to
handle much less data and allows for an analysis over larger time frames.
\item {\bf k-item Sliding Window}\newline  The k-item Sliding Window methods
retrieves all messages that match the query exactly one time. Each time k new messages are
available matching the given query a document containing those k messages
is retrieved. This method can lead to high data volume and needs constant
monitoring of recently posted messages matching the search term.
\end{itemize}
\end{definition}

We considered the trending topics on Twitter a good set of input queries for
our evaluation approach. Trending topics often cover a variety of recently
talked about topics which due to its recent nature may be of high interest for
further processing. Using the retrieved trending topics given in Table
\ref{tbl:terms} as input queries for the evaluation, the set of queries was executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame starting from the moment the topics were identified as trending topics. We chose the Temporal Sliding Window method for data acquisition because of the expected data volume generated by trending topics as search terms and the long term nature of our evaluation approach. We have then evaluated the results
with respect to several measures:
